### 2014-10-11 Neutral_simulPow.Rmd
Restrict q<=10 for growthCurve comparison

g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type)
g+theme_bw()

@@

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
#ggsave("power_DifReplacement.png", width=6,height=6,units="in",dpi=600)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

@@

# Test usign glm whic factors influence power

@@

```{r infoDim_Ttest, eval=F,echo=F,message=T,warning=T}
setwd("Simul")
#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
# 256 = 7 points for Dq
#
#cc <- powerNeutral_1T_D1(sim1,7,1)
# 
# Dq1 <- readNeutral_calcDq("neuFish65_256T100mfOrd.txt")
# 
# D1 <- DqT[DqT$q==1,]
# dd <- D1[121:122,]
# 
# compareTwoCurvesT(dd$Type,dd$Dq,dd$SD.Dq,5)
# 
# dd <- D1[c(41,45),]
# 
# compareTwoCurvesT(dd$rep,dd$Dq,dd$SD.Dq,5)

@@

# En vez de hacer merge fijarse donde genero parametros de simulacion!!!!!!!!
pad <- merge(pow_AD,simul,by.x=c("Side","NumSp"),by.y=c("side","nsp") )

g <- ggplot(pad,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type)
g+theme_bw()

@@

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Type,DifR),hh)
#ggsave("power_DifReplacement.png", width=6,height=6,units="in",dpi=600)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

@@

@@

@@

```{r more_simul512_LogSerParms, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

@@

>>>>

g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="Disp - Mort")

g+theme_bw()
ggsave("powAD_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

@@

comp_AD$spMeta <- ceiling(as.numeric(comp_AD$NumSp)*1.33)

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Type,DifR),hh)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)+
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab(bquote(Delta ~"Replacement rate")) +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

ggsave("powAD_DifReplacement.png", width=6,height=6,units="in",dpi=600)

require(pander)
pandoc.table(c2,style="grid")

@@

# Test usign glm which factors influence power

@@

```{r infoDim_Ttest, eval=F,echo=F,message=T,warning=T}
setwd("Simul")
#sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
# 256 = 7 points for Dq
#
#cc <- powerNeutral_1T_D1(sim1,7,1)

@@

require(ggplot2)
pow_TD1$MeanSp <- as.numeric(pow_TD1$MeanSp)
pow_TD1$power <- as.numeric(pow_TD1$power)
pow_TD1$typeI <- as.numeric(pow_TD1$typeI)
# Add number of species in the metacommunity
pow_TD1$spMeta <- ceiling(as.numeric(pow_TD1$NumSp)*1.33)

g <- ggplot(pow_TD1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+theme_bw()

ggsave("powTD1_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

g <- ggplot(pow_TD1,aes(x=spMeta,y=typeI)) + geom_point(shape=19,aes(size=power)) + facet_grid(Side ~ Type)
g+theme_bw()

@@

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
comp_TD1$spMeta <- ceiling(as.numeric(comp_TD1$NumSp)*1.33)

c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))

c2 <- ddply(c1,.(spMeta,Type,DifR),hh)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab(bquote(Delta ~"Replacement rate")) +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

ggsave("powTD1_DifReplacement.png", width=6,height=6,units="in",dpi=600)

# Calculate TypeI error in fuction of replacement rate
c1 <- with(comp_TD1,comp_TD1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
names(c3)[4]<-"typeI"
g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+theme_bw()

@@

The power of D1 in combination with a T-test is relatively low with a maximun of 0.6 for

@@

```{r power_PlotGC, eval=F,echo=F,message=T,warning=T}

require(ggplot2)
pow_GC1$MeanSp <- as.numeric(pow_GC1$MeanSp)
pow_GC1$power <- as.numeric(pow_GC1$power)
pow_GC1$typeI <- as.numeric(pow_GC1$typeI)

# Add number of species in the metacommunity
pow_GC1$spMeta <- ceiling(as.numeric(pow_GC1$NumSp)*1.33)

g <- ggplot(pow_GC1,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=Type)) + facet_grid(Side ~ . ) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="") 
g+theme_bw()
ggsave("powGC_spMeta_Side.png", width=6,height=6,units="in",dpi=600)

# Calculate power in fuction of replacement rate difference
comp_GC1$spMeta <- ceiling(as.numeric(comp_GC1$NumSp)*1.33)

c1 <- with(comp_GC1,comp_GC1[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))

c2 <- ddply(c1,.(spMeta,Type,DifR),hh)

g <- ggplot(c2,aes(x=DifR,y=power)) + geom_point(shape=19,position = position_jitter(height = .05),aes(colour=as.factor(Type))) + facet_grid( spMeta ~ .) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab(bquote(Delta ~"Replacement rate")) +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="")

g+ scale_x_log10(breaks=c(0.001,0.01,0.09,1))+theme_bw()

ggsave("powGC_DifReplacement.png", width=6,height=6,units="in",dpi=600)

@@

```{r more_simul512_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

@@

```{r more_simul256_LogSerParms, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

simul <- rbind(simul,simulNeutral_1Time(8,256,500,"L",20,F))
simul <- rbind(simul,simulNeutral_1Time(64,256,500,"L",20,F))
simul <- rbind(simul,simulNeutral_1Time(256,256,500,"L",20,F))

setwd(oldcd)
save.image()
```
Using the GC with q<=10

```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
setwd("Simul")
# sim1 <- data.frame(nsp=65,side=256,time=100,meta="L",spMeta=87,rep=3)
#
#cc <- powerNeutral_1T_GC(simul[1,],3,0.2,0.04,0.001,10)

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0.2,0.04,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

  pow_GCq10 <- rbind(pow_GCq10, cc[[i]]$pow_AD)
  comp_GCq10<- rbind(comp_GCq10,cc[[i]]$comp_AD)
  }
